\chapter{May 16, 2019}

\section{ICRC Planning}
Timeline:
\begin{itemize}
    \itemsep-0.85em 
    \item Soft deadline for first drafts to be uploaded to Google Drive / overleaf: June 4.
    \item Final deadline for new analyses approved for unblinding: June 6.
    \item Hard deadline for first drafts to be uploaded to Google Drive / overleaf: June 11
    \item Final deadline for new plots to be shown in the analysis call: June 13.
    \item Final drafts of proceedings for collaboration review: June 25 (3 weeks before ICRC deadline)
    \item Final ICRC deadline for uploading papers is July 16.
\end{itemize}

June 4 is 2.5 weeks away, to iterate locally, try to send drafts beforehand (two weeks from today).

Unclear of what ``final deadline for new plots to be shown'' means, Raamis is following up with Ignacio or Segev


\subsection{Gravitational Waves (Raamis)}
For upper limits, Raamis might try to get on the next Neutrino sources call to discuss the new way to calculate upper limits, so that he might be able to put the new upper limits in the ICRC proceedings. 
\begin{itemize}
    \itemsep-0.85em 
    \item Unblinded skymaps with neutrinos and 90\% contours (archival and realtime)
    \item Background TS distributions, or possibly fit vs. injected flux
    \item (Updated) upper limits
    \item Table with all of the results
    \item Science / citation heavy introduction
\end{itemize}

\subsection{ANITA: Collaboration (Alex)}
ICRC proceeding that will be pretty much a copy of the journal paper. Possibly keep interpretation section short. I'll try to discuss with Anastasia next week. Could potentially get more into the likelihood analyses if it's easy. 

\subsection{ANITA: Few Author (Ibrahim)}
Hopefully we will have the few author paper out, and then we could essentially just promote that paper in the ICRC writeup. 

\subsection{FRB (Alex)}
Highlight the journal paper with representative plots from the L2 analysis and Ali's analysis. Include text about the prospects for future analyses. Could discuss realtime and reference fast response 

\subsection{Fast Response (Justin)}
Justin can lead paper writing. Plots / things that we need:
\begin{itemize}
    \itemsep-0.85em 
    \item p-value distribution
    \item Tables with all of the results
    \item Zoomed in skymaps of certain analyses
    \item False alarm rate plot
    \item Average latency or computing time
    \item Some performance plots
    \item Outlook for scanning source localization uncertainties
\end{itemize}

\subsection{DECO (Alex)}
Blake is happy to help with the writing, and Justin is back June 16th. I will aim to have a draft with Blake by the time Justin gets back. I will see if I can get Blake on the author list
\begin{itemize}
    \itemsep-0.85em 
    \item About a third general description and updating the world map (Blake?) Maybe avoid total user count in favor of world map
    \item About a third on CNN stuff, citing the paper
    \item About a third on new stuff (simulation and experimental). For the experimental stuff, let's try to get them classified and then compare the distributions. Probably avoid efficiencies in favor of classifications (if they agree). Maybe rate with and without a source side by side comparison
\end{itemize}


